VM-Centric Snapshot Deduplication\\ for Cloud Data Backup

### 2015-03-14 snapshot_system/mass.tex
added flushend
re

\usepackage{mathptmx}
%\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,positioning,decorations.pathmorphing}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{sansmath}
\usepackage{booktabs}
\usepackage{soul}
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

@@

\author{
\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{2}\IEEEauthorrefmark{1}, Daniel Agun\IEEEauthorrefmark{1}, 
Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
Hong Tan\IEEEauthorrefmark{3}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of California at Santa Barbara}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Pure Storage Inc.}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Alibaba Inc.}
%Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$,
%Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
%   {\normalsize $^\star$UC Santa Barbara}\\
%   {\normalsize$^\dagger$Alibaba.com}

>>>>

\usepackage{mathptmx}
%\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{multirow}
\usepackage{array}
\usepackage{breqn}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,positioning,decorations.pathmorphing}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{sansmath}
\usepackage{booktabs}
\usepackage{soul}
\usepackage{flushend} %automatically balance columns of last page
\pgfplotsset{compat=1.5}
\DeclareGraphicsExtensions{.pdf}

@@

\author{
\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{2}, Daniel Agun\IEEEauthorrefmark{1}, 
Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
Hong Tang\IEEEauthorrefmark{3}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of California at Santa Barbara}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Pure Storage Inc.}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Alibaba Inc.}
%Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$,
%Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
%   {\normalsize $^\star$UC Santa Barbara}\\
%   {\normalsize$^\dagger$Alibaba.com}

### 2015-03-14 snapshot_system/mass_abs.tex
re

\begin{abstract}
Data deduplication is important  for snapshot backup of virtual machines (VMs)
because of excessive redundant content.  Fingerprint search for source-side duplicate 
detection is resource intensive when the backup service for VMs  is co-located with  other 
cloud services.  This paper presents the design and implementation of
a low-profile VM-centric backup service with  a tradeoff 
for a competitive deduplication efficiency while using small computing resources, 
suitable for running on a converged cloud architecture that cohosts  many other services.
This cluster-based service restricts global deduplication and 
separates popular chunks with non-popular ones.   
The  developed optimization includes similarity-guided local search 
for  the improved overall deduplication effectiveness 
and  VM-centric file system block management for the increased VM snapshot availability.  
%deduplication under popular chunks with extra replication support.
%and use an approximate method for fast and simplified snapshot deletion.
%by separating popular chunks and associating  file system blocks with one VM for non-popular chunks.
This  paper  describes an evaluation of this VM-centric scheme to assess  its deduplication 
efficiency, resource usage,  and fault tolerance.

>>>>

\begin{abstract}
Data deduplication is important  for snapshot backup of virtual machines (VMs)
because of excessive redundant content.  Fingerprint search for source-side duplicate 
detection is resource intensive when the backup service for VMs  is co-located with  other 
cloud services.  This paper presents the design and implementation of
a fast VM-centric backup service with  a tradeoff 
for a competitive deduplication efficiency while using small computing resources, 
suitable for running on a converged cloud architecture that cohosts  many other services.
The  developed optimization includes similarity-guided local search 
for  the improved overall deduplication effectiveness 
and  VM-centric file system block management for the increased VM snapshot availability.  
%deduplication under popular chunks with extra replication support.
%and use an approximate method for fast and simplified snapshot deletion.
%by separating popular chunks and associating  file system blocks with one VM for non-popular chunks.
This  paper  describes an evaluation of this VM-centric scheme to assess  its deduplication 
efficiency, resource usage,  and fault tolerance.
